The LHC as a Neutrino-Ion Collider

### 2023-11-16 referee/referee-reply.tex

\item{\it  p.5 l.49 col 1 and col 2 (“AdvSND” and “FLArE”) Can you put a reference about these experiments? Did you take the info from ref [10]?}

We have added the original flare proposal paper as well as the whitepaper (ref[10]) to the FLArE section. For AdvSND, we have added included the whitepaper

\item{\it p.6 l. 50-53 col.2 “Here we neglect efficiency .. simulation.” I am aware that this might be difficult to simulate at this stage but I think this effect is non-negligible due to misidentification ( a large background could enter this sample). Can you comment further on it? In addition, some guesses on misidentification capabilities can be drawn by the current FASER and SND@CERN capabilities.}

Indeed, misidentification is not expected to be negligible. While there are no detailed studies of charm tagging efficiencies at the FPF, as we point out in the paper charm tagging can be done by through multiple methods, including reconstructing the topology of D-meson decays, and through dimuon events. With multiple techniques, one can draw the conclusion that charm-tagging efficiency is not small.
{\color {red} [MF: looking for quantitative perofrmances/efficiencies, can't find anything. Is there more we can say? We could look at older experiments]}

@@

\item{\it p.9 l. 41-43 col.2 “We note that … in our estimation.” (see also the conclusions p. 27 l. 52-55 col.1) I am puzzled by this statement. It is well known that flux systematics in Faser and SND@CERN play a prominent role and set the normalization (and shape?) of eqn 2.12. How can you ignore such an important effect in your analyses? Even if the PDF constraints are marginally affected by the normalization of the neutrino flux, some of your considerations about the on-axis (faser and faser2) versus the off-axis experiments (SND@CERN and its upgrades) may be affected by flux uncertainties. Can you comment on it in the paper?}

Indeed, neutrino flux uncertainties are well established, and the shape and normalization of the flux can vary widely between different models. It is important to note that neutrino measurements actually constrain the product of flux and cross-section - each of these components brings an uncertainty with it, and a full analysis with real data would constrain them simultaneously. We wish to motivate this joint analysis by calculating the  impact that FPF data can bring to a PDF fit. In this sense, by taking the flux to be known we can understand the full reach of FPF data on cross-section measurements, analogous to what was done in 2309.10417. Moreover, projections of FPF data on flux measurements has shown that HL-LHC data can bring flux uncertainties to a sub-percent level. We thank the referee for this important point and add the following paragraph after we introduce the flux model in the middle of section 2.3.

"As pointed out in Ref.~\cite{Kling:2021gos} there are notable neutrino flux uncertainties, as various event generators do not agree on the forward parent hadron spectra. The spread of the generators' predictions can be taken as a means of flux uncertainty, in which case there is a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum --- if left unresolved this would be a significant systematic. Indeed, there are already projections of FPF measurements which would reduce this uncertainty to the sub-percent level~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}. However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other. In a full analysis, they would be constrained simultaneously in a joint measurement. In our study, we aim to understand the full impact of FPF data on the PDF fit, thus motivating this future joint measurement. To this aim, we take the neutrino flux to be known and focus on the irreducible systematics associated with event reconstruction."

### 2023-11-16 journal_sub/sec-dis-pseudodata.tex
small corrections

%
As pointed out in Ref.~\cite{Kling:2021gos} there are notable neutrino flux uncertainties, as various event generators do not agree on the forward parent hadron spectra. 
%
The spread of the generators' predictions can be taken as a means of flux uncertainty, in which case there is a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum --- if left unresolved this would be a significant systematic. Indeed, there are already projections of FPF measurements which would reduce this uncertainty~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
%
However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other. In a full analysis,  they would be constrained simultaneously in a joint measurement.
%
In our study, we aim to understand the full impact of FPF data on the PDF fit, thus motivating this future joint measurement.
%
To this aim, we take the neutrino flux to be known and focus on the irreducible systematics associated with event reconstruction.

>>>>

%
As pointed out in Ref.~\cite{Kling:2021gos} there are notable neutrino flux uncertainties, as various event generators do not agree on the forward parent hadron spectra. 
%
The spread of the generators' predictions can be taken as a means of flux uncertainty, in which case there is a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum --- if left unresolved this would be a significant systematic. Indeed, there are already projections of FPF measurements which would reduce this uncertainty to the sub-percent level~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
%
However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other. In a full analysis,  they would be constrained simultaneously in a joint measurement.
%
In our study, we aim to understand the full impact of FPF data on the PDF fit, thus motivating this future joint measurement.
%
To this aim, we take the neutrino flux to be known and focus on the irreducible systematics associated with event reconstruction.
